```{r}
#| eval: TRUE
#| include: FALSE

    source('../../script/_load_libraries.R')
    source('../../script/01_gather_data.R')
    
```

# Review #0001 {.unnumbered}

## Short Summary

```{r}
#| echo: FALSE
#| eval: TRUE
#| output: asis

    source('../../script/02_print_short_summary.R')
```

## Authors

```{r}
#| echo: FALSE
#| eval: TRUE
#| output: asis

    source('../../script/03_print_affiliations.R')
```

## Keywords

```{r}
#| echo: FALSE
#| eval: TRUE
#| output: asis

    source('../../script/04_print_keywords.R')
```

## Research Methods

```{r}
#| echo: FALSE
#| eval: TRUE
#| output: asis

    source('../../script/05_print_research_methods.R')
```

## Source References

## Databases

#### Search Databases

#### Medical Datasets

## Classification

#### Patient Types

#### Decision Levels

#### Level of Integration

## Constraints

## Bias Assessment

## Focus Review

#### Summary

Dacre Knight et al. [@x034] conducted a meta-narrative literature review for Artificial Intelligence and Machine Learning technologies implemented in healthcare. The researchers define three types of studies: pre-pilot, pilot and implemented. Major databases were searched on August 14, 2020, and only the publications of the third type were selected for deeper review. The review paper highlights the advantages and obstacles of using AI technologies in healthcare. The authors consider their work's limitations and outline future research directions.

#### Objectives

The artificial intelligence and machine learning approaches are uncharted territory in the optimal scheduling.

#### Methods

The authors of systematic review of publications starting from August 2020. The reviews of literature were conducted by two independent specialists per each article.

#### Results

Areas of AI application are: double-booking, missed appointment risk, wait time, disease-type matching performance, scheduling efficiency, examination length prediction, and surgical operation time.

#### Conclusions

Proved the AI competence and found new revenues for development

#### Notes

-   Studies split into three stages: pre-pilot, pilot, implementation;
-   11 implemented works;
-   general statements, low-on-insights reveiw;
-   2 reviewers + consultant investigator
